\begin{abstract}
We perform a safety and progress analysis of a \emph{map-less} path planner and path-tracking controller for an autonomous car racing on a circuit.
%
Here, \emph{map-less} means that the  planner operates purely based on the current on-board sensor data to follow the racing track.
%
In contrast, a \emph{map-based} planner uses both sensor data and a map (either known apriori or built at runtime) to localize the vehicle within the map and perhaps plan a racing line.
%
Our planner chooses a path on the Voronoi diagram of the current perception and our controller uses \emph{pure-pursuit} to track the path.
% Reveals identity?
A version of our planner and controller won the Generalized RAcing Intelligence Competition (GRAIC) which includes dynamic obstacles as well.
%
Our safety and performance analysis has two parts.
%
The first part gives sufficient conditions such that the plan is consistent with a map-based plan computed from the Voronoi diagram of the full map of the racing track.
%
The second part proves the safety and progress with respect to the map-based plan.
%
Therefore, the map is needed for the proofs, but not needed by the planner or the controller.
%
In particular, given any map and vehicle, if the sufficient conditions hold, then we can conclude that the map-less planner and controller can drive the vehicle safely and finish a lap.
%
As examples, we prove the safety and progress of our planner and controller for five different circuits.
%
In addition, we demonstrate that our implemented planner and controller work well for a wide variety of circuits both in a simulation environment and on a scaled down autonomous vehicle in an office environment.

\end{abstract}