\section{Guarantees of safety and progress}
\label{sec:guarantees}

In this section we perform a formal analysis of the motion planner.
%
We prove that the car does not hit any of the track boundaries and will successfully complete one or more laps in several circuit tracks.


In the first part, we prove that the \emph{local Voronoi diagram} is consistent with the \emph{global Voronoi diagram} under sufficient conditions.
%
Thus we can predict that the planner's output, which is a path on the local Voronoi diagram, is a path on the global Voronoi diagram.


In the second part, we model the closed-loop dynamics of the car by composing the global Voronoi diagram, the path-tracking controller, and the bicycle model of a car.
%
We compute the \emph{reachable set} of the closed-loop behavior over a finite time horizon.
%
The reachable set includes the set of states visited by the trajectories starting from an initial set of states.
%
We demonstrate that the reachable set does not overlap with any of the track boundaries and finishes a lap.
%
If the reachable set achieves a \emph{fixed point} over a finite time, i.e. does not discover new states after a time step, then we can infer that the car will continue to finish more laps safely for any number of laps.
%
That is, with a finite computation we can prove safety and progress for an infinite time horizon.

\subimport{}{4-1-voronoi.tex}
\subimport{}{4-2-bicycle_model.tex}
\subimport{}{4-3-system_model.tex}
\subimport{}{4-4-reachable-set.tex}


